The transiting dust clumps in the evolved disk of the Sun-like UXor RZ~Psc

### 2016-12-09 ms.tex
resubmission

% yearly-lc.pro
\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=\textwidth]{figs/yearly-2004.eps}
    \caption{WASP and KELT-North data. Photometry is shown in dimensionless form,
      relative to a quiescent level of 1, and was converted from observed magnitudes as
      described in the text.}\label{fig:waspkelt}
  \end{center}
\end{figure*}

@@

% yearly-zoom.pro
\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=\textwidth]{figs/yearly-zoom.eps}
    \caption{WASP and KELT-North data, focussing on dimming events. The vertical and
      horizontal scales in each sub-panel are the same.}\label{fig:waspkeltzoom}
  \end{center}
\end{figure*}

@@

\subsection{Infrared}\label{ss:ir}

@@

% visir analysis, p97-results
\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/RZ-Psc.eps}
    \caption{Flux density distribution of RZ~Psc, including 2MASS, WISE, AKARI, VISIR,
      and IRAS data and their (approximate) year of observation. The dark blue line shows
      a stellar photosphere model at the approximate stellar temperature of 5350K, and
      the light blue line a 500K blackbody. The latter is not a fit, but an approximate
      continuum level that illustrates that the WISE 3.4 and 22$\mu$m photometry cannot
      both be accounted for with a single blackbody, if the silicate feature seen with
      VISIR was present in 2010.}\label{fig:sed}
  \end{center}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=\textwidth]{figs/wise-var.eps}
    \caption{WISE epoch photometry at 3.4, 4.6, 12, and 22$\mu$m (W1, W2, W3, and W4, in
      magnitudes). The left panel shows the time variation in W1 over 5.5
      years. Subsequent panels show how W1 correlates with W2, W3, and W4, which do not
      have observations at all W1 epochs. The dashed lines show the slope expected for
      constant disk flux variation with wavelength (the variation is smaller in W1/2
      because the total flux is not dominated by the disk).}\label{fig:wisevar}
  \end{center}
\end{figure*}

@@

% period-search.pro
\begin{figure}
\begin{center}
\hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/auto.eps}
\caption{Discrete autocorrelation function for yearly WASP and KELT-North data, computed
  for lags between 10-155 days). The second and third lines from the top show all data,
  and 2006-excluded data. The topmost line shows the number of years that show a peak
  more than 3$\sigma$ above the clipped DACF mean within each 5 day bin. The peak at 70
  days is 7 years, the dashed line is zero, and the y-axis scale is shown to the
  right.}\label{fig:auto}
\end{center}
\end{figure}

@@

% plot_lc_dips_dts.py
% \begin{figure*}
  % \begin{center}
  %   \hspace{-0.cm} \includegraphics[width=\textwidth]{figs/lc_dips_dts.ps}
    % \caption{Iterative dimming event finding. The right part of the plot shows the same
    %   time series as Figure \ref{fig:waspkelt}, with the identified dimming events shown
    %   as boxes. The time differences between these events is shown on the left side of
    %   the plot. The boxes are transparent, so the density is a measure of the power at a
    %   given period.}\label{fig:iter}
  % \end{center}
% \end{figure*}

@@

% plot_hist_sim.py
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/hist_single.ps}
    \caption{Power at a given period from the iterative event finding. The solid line
      shows the power from the data, and is the same in each panel. The dashed lines show
      the mean and $\pm$1$\sigma$ power from simulated dimming events, which from top to
      bottom are: random, periodic between 64 and 75 days with 3 repeats, and periodic at
      64 days with 10 repeats.}\label{fig:hist}
  \end{center}
\end{figure}

@@

% gradients.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/gradients.eps}
    \caption{Gradient and minimum flux measured from individual nights'
      observations. Open circles have gradients significantly different from zero, and a
      symbol size proportional to the inverse of the gradient uncertainty. Dots are
      consistent with zero slope. The lines show the gradients implied by the velocities
      for circular orbits at 0.3, 1, 10, and 100au.}\label{fig:grad}
  \end{center}
\end{figure}

@@

% gradients.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/sma.eps}
    \caption{Semi-major axes estimated from the light curve gradients in Figure
      \ref{fig:grad}. Open circles have gradients significantly different from zero, and
      a symbol size proportional to the inverse of the gradient uncertainty. Dots are
      consistent with zero slope. The stellar radius (grey dashed line) has been
      estimated as Solar. Because gradients may have lower minimum fluxes they can move
      down along lines parallel to the solid lines. Points near or above the blue line
      are consistent with zero light curve gradient.}\label{fig:sma}
  \end{center}
\end{figure}

@@

% rcl-a.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/rcl-a.eps}
    \caption{Clump properties assuming circular orbits for a range of dimming event
      durations (as labelled). The brown region marks the approximate location of the
      RZ~Psc asteroid belt (or the inner edge of a more extended disk). The blue shaded
      region shows the range of Herbig Ae inner disk edge radii. The dashed line shows
      where a clump has an azimuthal extent similar to the scale height of a typical
      gas-rich disk.}\label{fig:rcla}
  \end{center}
\end{figure}

@@

% sedcomp.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/spcomp.eps}
    \caption{The SED of RZ~Psc in comparison with other young disk-hosting stars. All
      SEDs are normalised to a common flux density at $H$ band. The triangles are AKARI
      and IRAS upper limits for RZ~Psc. Measurements we made at different times, so the
      apparent discrepancy between the WISE detection at 22$\mu$m and the AKARI upper
      limit at 18$\mu$m is an indicator of IR variability (see section
      \ref{s:data}\ref{ss:ir}).}\label{fig:spcomp}
  \end{center}
\end{figure}

@@

Finally, the mid-IR variability discussed in section \ref{s:data}\ref{ss:ir} provides a
measure of the changing emitting area of the disk around RZ~Psc, and thus potentially
information about the disk structure and status. Figure \ref{fig:wisevar} shows that for
the epochs where contemporaneous 3-22$\mu$m photometry exists there is no evidence of
``seesaw'' variability over 6 months, but that strong conclusions are limited by a lack
of data. Over 5 years the 3-5$\mu$m disk flux varied by about a factor of two, with no
major changes in the behaviour of the optical light curve. However, given that the bulk
of the disk emission probably originates from material that is not occulting the star,
direct links between the optical and IR behaviour is not necessarily expected. Indeed,
towards young stars hosting gas-rich disks, both correlated and uncorrelated optical/IR
variability is seen \cite{2014AJ....147...82C}. Similarly, the IR flux of bright warm
debris disks has been seen to vary strongly while the optical brightness remains constant
\cite{2015ApJ...805...77M}. The main benefit of more intensive IR monitoring would be to
search for mid-IR ``see-saw'' variability, because it would provide evidence that the
disk around RZ~Psc has a significant radial extent.

@@

% export from cartoon.key, cropped with pdfcrop
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{figs/cartoon-crop.ps}
    \caption{Cartoon showing possible origins of dippers and UXors, and why Sun-like
      stars may only rarely show analogous behaviour. In each case the star, magnetic
      dipole, and rotation axis are shown at the left (the stellar magnetic field is not
      necessarily always tilted with respect to the disk). Possible disk structures
      viewed edge-on to the right. (\emph{top}) low-mass stars (dippers) are occulted by
      co-rotating material that is accreting on to the star, and the dust sublimation
      radius is interior to corotation \cite{2016arXiv160503985B}. (\emph{middle})
      Sun-like stars are rarely seen as dippers or UXors because i) dust sublimates
      outside corotation (represented by the grey accretion column in the upper half
      \cite{2016arXiv160503985B}), or ii) material lifted by turbulence is shadowed by
      the outer disk (spiral in the lower half). (\emph{bottom}) Herbig Ae/Be stars
      (UXors) are occulted by turbulence that appears above self-shadowed disks
      \cite{2003ApJ...594L..47D}.}\label{fig:cartoon}
  \end{center}
\end{figure}

@@

\textbf{Contributions:} GMK initiated the project, collated data, did most of the
analysis, and wrote the paper. MAK contributed to the time-series analysis and conceived
the iterative event finding method. KGS provided independent SED models to test for a UV
excess. As members of the KELT collaboration, JP, JER, RJS, and KGS acquired the
time-series photometry. All co-authors provided input on the style and content of the
manuscript.

@@

\bibliography{../ref} \bibliographystyle{vancouver}

@@

>>>>

% yearly-lc.pro
\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=\textwidth]{yearly-2004.eps}
    \caption{WASP and KELT-North data. Photometry is shown in dimensionless form,
      relative to a quiescent level of 1, and was converted from observed magnitudes as
      described in the text.}\label{fig:waspkelt}
  \end{center}
\end{figure*}

@@

% yearly-zoom.pro
\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=\textwidth]{yearly-zoom.eps}
    \caption{WASP and KELT-North data, focussing on dimming events. The vertical and
      horizontal scales in each sub-panel are the same.}\label{fig:waspkeltzoom}
  \end{center}
\end{figure*}

@@

\subsection{Infrared}\label{ss:irvar}

@@

% visir analysis, p97-results
\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{RZ-Psc.eps}
    \caption{Flux density distribution of RZ~Psc, including 2MASS, WISE, AKARI, VISIR,
      and IRAS data and their (approximate) year of observation. The dark blue line shows
      a stellar photosphere model at the approximate stellar temperature of 5350K, and
      the light blue line a 500K blackbody. The latter is not a fit, but an approximate
      continuum level that illustrates that the WISE 3.4 and 22$\mu$m photometry cannot
      both be accounted for with a single blackbody, if the silicate feature seen with
      VISIR was present in 2010.}\label{fig:sed}
  \end{center}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=\textwidth]{wise-var.eps}
    \caption{WISE epoch photometry at 3.4, 4.6, 12, and 22$\mu$m (W1, W2, W3, and W4, in
      magnitudes). The left panel shows the time variation in W1 over 5.5
      years. Subsequent panels show how W1 correlates with W2, W3, and W4, which do not
      have observations at all W1 epochs. The dashed lines show the slope expected for
      constant disk flux variation with wavelength (the variation is smaller in W1/2
      because the total flux is not dominated by the disk).}\label{fig:wisevar}
  \end{center}
\end{figure*}

@@

% period-search.pro
\begin{figure}
\begin{center}
\hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{auto.eps}
\caption{Discrete autocorrelation function for yearly WASP and KELT-North data, computed
  for lags between 10-155 days). The second and third lines from the top show all data,
  and 2006-excluded data. The topmost line shows the number of years that show a peak
  more than 3$\sigma$ above the clipped DACF mean within each 5 day bin. The peak at 70
  days is 7 years, the dashed line is zero, and the y-axis scale is shown to the
  right.}\label{fig:auto}
\end{center}
\end{figure}

@@

% plot_lc_dips_dts.py
% \begin{figure*}
  % \begin{center}
  %   \hspace{-0.cm} \includegraphics[width=\textwidth]{lc_dips_dts.ps}
    % \caption{Iterative dimming event finding. The right part of the plot shows the same
    %   time series as Figure \ref{fig:waspkelt}, with the identified dimming events shown
    %   as boxes. The time differences between these events is shown on the left side of
    %   the plot. The boxes are transparent, so the density is a measure of the power at a
    %   given period.}\label{fig:iter}
  % \end{center}
% \end{figure*}

@@

% plot_hist_sim.py
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{hist_single.ps}
    \caption{Power at a given period from the iterative event finding. The solid line
      shows the power from the data, and is the same in each panel. The dashed lines show
      the mean and $\pm$1$\sigma$ power from simulated dimming events, which from top to
      bottom are: random, periodic between 64 and 75 days with 3 repeats, and periodic at
      64 days with 10 repeats.}\label{fig:hist}
  \end{center}
\end{figure}

@@

% gradients.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{gradients.eps}
    \caption{Gradient and minimum flux measured from individual nights'
      observations. Open circles have gradients significantly different from zero, and a
      symbol size proportional to the inverse of the gradient uncertainty. Dots are
      consistent with zero slope. The lines show the gradients implied by the velocities
      for circular orbits at 0.3, 1, 10, and 100au.}\label{fig:grad}
  \end{center}
\end{figure}

@@

% gradients.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{sma.eps}
    \caption{Semi-major axes estimated from the light curve gradients in Figure
      \ref{fig:grad}. Open circles have gradients significantly different from zero, and
      a symbol size proportional to the inverse of the gradient uncertainty. Dots are
      consistent with zero slope. The stellar radius (grey dashed line) has been
      estimated as Solar. Because gradients may have lower minimum fluxes they can move
      down along lines parallel to the solid lines. Points near or above the blue line
      are consistent with zero light curve gradient.}\label{fig:sma}
  \end{center}
\end{figure}

@@

% rcl-a.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{rcl-a.eps}
    \caption{Clump properties assuming circular orbits for a range of dimming event
      durations (as labelled). The brown region marks the approximate location of the
      RZ~Psc asteroid belt (or the inner edge of a more extended disk). The blue shaded
      region shows the range of Herbig Ae inner disk edge radii. The dashed line shows
      where a clump has an azimuthal extent similar to the scale height of a typical
      gas-rich disk.}\label{fig:rcla}
  \end{center}
\end{figure}

@@

% sedcomp.pro
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{spcomp.eps}
    \caption{The SED of RZ~Psc in comparison with other young disk-hosting stars. All
      SEDs are normalised to a common flux density at $H$ band. The triangles are AKARI
      and IRAS upper limits for RZ~Psc. Measurements we made at different times, so the
      apparent discrepancy between the WISE detection at 22$\mu$m and the AKARI upper
      limit at 18$\mu$m is an indicator of IR variability (see section
      \ref{s:data}\ref{ss:irvar}).}\label{fig:spcomp}
  \end{center}
\end{figure}

@@

Finally, the mid-IR variability discussed in section \ref{s:data}\ref{ss:irvar} provides a
measure of the changing emitting area of the disk around RZ~Psc, and thus potentially
information about the disk structure and status. Figure \ref{fig:wisevar} shows that for
the epochs where contemporaneous 3-22$\mu$m photometry exists there is no evidence of
``seesaw'' variability over 6 months, but that strong conclusions are limited by a lack
of data. Over 5 years the 3-5$\mu$m disk flux varied by about a factor of two, with no
major changes in the behaviour of the optical light curve. However, given that the bulk
of the disk emission probably originates from material that is not occulting the star,
direct links between the optical and IR behaviour is not necessarily expected. Indeed,
towards young stars hosting gas-rich disks, both correlated and uncorrelated optical/IR
variability is seen \cite{2014AJ....147...82C}. Similarly, the IR flux of bright warm
debris disks has been seen to vary strongly while the optical brightness remains constant
\cite{2015ApJ...805...77M}. The main benefit of more intensive IR monitoring would be to
search for mid-IR ``see-saw'' variability, because it would provide evidence that the
disk around RZ~Psc has a significant radial extent.

@@

% export from cartoon.key, cropped with pdfcrop
\begin{figure}
  \begin{center}
    \hspace{-0.5cm} \includegraphics[width=0.7\textwidth]{cartoon-crop.ps}
    \caption{Cartoon showing possible origins of dippers and UXors, and why Sun-like
      stars may only rarely show analogous behaviour. In each case the star, magnetic
      dipole, and rotation axis are shown at the left (the stellar magnetic field is not
      necessarily always tilted with respect to the disk). Possible disk structures
      viewed edge-on to the right. (\emph{top}) low-mass stars (dippers) are occulted by
      co-rotating material that is accreting on to the star, and the dust sublimation
      radius is interior to corotation \cite{2016arXiv160503985B}. (\emph{middle})
      Sun-like stars are rarely seen as dippers or UXors because i) dust sublimates
      outside corotation (represented by the grey accretion column in the upper half
      \cite{2016arXiv160503985B}), or ii) material lifted by turbulence is shadowed by
      the outer disk (spiral in the lower half). (\emph{bottom}) Herbig Ae/Be stars
      (UXors) are occulted by turbulence that appears above self-shadowed disks
      \cite{2003ApJ...594L..47D}.}\label{fig:cartoon}
  \end{center}
\end{figure}

@@

\textbf{Contributions:} GMK initiated the project, collated data, did most of the
analysis, and wrote the paper. MAK contributed to the time-series analysis and conceived
the iterative event finding method. KGS provided independent SED models to test for a UV
excess. As members of the KELT collaboration, JP, JER, RJS, and KGS acquired the
time-series photometry. MCW was a co-I on the proposal to obtain the VISIR data. All
co-authors provided input on the style and content of the manuscript.

@@

%\bibliography{../ref} \bibliographystyle{vancouver}

@@

\begin{thebibliography}{10}

\bibitem{2001ApJ...553L.153H}
{Haisch} KE Jr, {Lada} EA, {Lada} CJ.
\newblock {Disk Frequencies and Lifetimes in Young Clusters}.
\newblock \apjl. 2001 Jun;553:L153--L156.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2001ApJ...553L.153H}.

\bibitem{1993prpl.conf.1253B}
{Backman} DE, {Paresce} F.
\newblock {Main-sequence stars with circumstellar solid material - The VEGA
  phenomenon}.
\newblock In: {Levy} EH, {Lunine} JI, editors. Protostars and Planets III;
  1993. p. 1253--1304.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1993prpl.conf.1253B}.

\bibitem{2002MNRAS.334..589W}
{Wyatt} MC, {Dent} WRF.
\newblock {Collisional processes in extrasolar planetesimal discs - dust clumps
  in Fomalhaut's debris disc}.
\newblock \mnras. 2002 Aug;334:589--607.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2002MNRAS.334..589W}.

\bibitem{2010RAA....10..383K}
{Krivov} AV.
\newblock {Debris disks: seeing dust, thinking of planetesimals and planets}.
\newblock Research in Astronomy and Astrophysics. 2010 May;10:383--414.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2010RAA....10..383K}.

\bibitem{2007ApJ...669.1298F}
{Fabrycky} D, {Tremaine} S.
\newblock {Shrinking Binary and Planetary Orbits by Kozai Cycles with Tidal
  Friction}.
\newblock \apj. 2007 Nov;669:1298--1315.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2007ApJ...669.1298F}.

\bibitem{1996Sci...274..954R}
{Rasio} FA, {Ford} EB.
\newblock {Dynamical instabilities and the formation of extrasolar planetary
  systems}.
\newblock Science. 1996 Nov;274:954--956.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1996Sci...274..954R}.

\bibitem{2005Natur.435..459T}
{Tsiganis} K, {Gomes} R, {Morbidelli} A, {Levison} HF.
\newblock {Origin of the orbital architecture of the giant planets of the Solar
  System}.
\newblock \nat. 2005 May;435:459--461.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2005Natur.435..459T}.

\bibitem{2010ApJ...717L..57M}
{Melis} C, {Zuckerman} B, {Rhee} JH, {Song} I.
\newblock {The Age of the HD 15407 System and The Epoch of Final Catastrophic
  Mass Accretion onto Terrestrial Planets Around Sun-like Stars}.
\newblock \apjl. 2010 Jul;717:L57--L61.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2010ApJ...717L..57M}.

\bibitem{2012MNRAS.425..657J}
{Jackson} AP, {Wyatt} MC.
\newblock {Debris from terrestrial planet formation: the Moon-forming
  collision}.
\newblock \mnras. 2012 Sep;425:657--679.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2012MNRAS.425..657J}.

\bibitem{2013MNRAS.433.2334K}
{Kennedy} GM, {Wyatt} MC.
\newblock {The bright end of the exo-Zodi luminosity function: disc evolution
  and implications for exo-Earth detectability}.
\newblock \mnras. 2013 Aug;433:2334--2356.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2013MNRAS.433.2334K}.

\bibitem{2009MNRAS.399..385B}
{Booth} M, {Wyatt} MC, {Morbidelli} A, {Moro-Mart{\'{\i}}n} A, {Levison} HF.
\newblock {The history of the Solar system's debris disc: observable properties
  of the Kuiper belt}.
\newblock \mnras. 2009 Oct;399:385--398.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2009MNRAS.399..385B}.

\bibitem{2014MNRAS.438.3299K}
{Kennedy} GM, {Murphy} SJ, {Lisse} CM, {M{\'e}nard} F, {Sitko} ML, {Wyatt} MC,
  et~al.
\newblock {Evolution from protoplanetary to debris discs: the transition disc
  around HD 166191}.
\newblock \mnras. 2014 Mar;438:3299--3309.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2014MNRAS.438.3299K}.

\bibitem{2014Sci...345.1032M}
{Meng} HYA, {Su} KYL, {Rieke} GH, {Stevenson} DJ, {Plavchan} P, {Rujopakarn} W,
  et~al.
\newblock {Large impacts around a solar-analog star in the era of terrestrial
  planet formation}.
\newblock Science. 2014 Aug;345:1032--1035.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2014Sci...345.1032M}.

\bibitem{1945ApJ...102..168J}
{Joy} AH.
\newblock {T Tauri Variable Stars.}
\newblock \apj. 1945 Sep;102:168.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1945ApJ...102..168J}.

\bibitem{1994AJ....108.1906H}
{Herbst} W, {Herbst} DK, {Grossman} EJ, {Weinstein} D.
\newblock {Catalogue of UBVRI photometry of T Tauri stars and analysis of the
  causes of their variability}.
\newblock \aj. 1994 Nov;108:1906--1923.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1994AJ....108.1906H}.

\bibitem{2011ApJ...733...50M}
{Morales-Calder{\'o}n} M, {Stauffer} JR, {Hillenbrand} LA, {Gutermuth} R,
  {Song} I, {Rebull} LM, et~al.
\newblock {Ysovar: The First Sensitive, Wide-area, Mid-infrared Photometric
  Monitoring of the Orion Nebula Cluster}.
\newblock \apj. 2011 May;733:50.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2011ApJ...733...50M}.

\bibitem{2014AJ....147...82C}
{Cody} AM, {Stauffer} J, {Baglin} A, {Micela} G, {Rebull} LM, {Flaccomio} E,
  et~al.
\newblock {CSI 2264: Simultaneous Optical and Infrared Light Curves of Young
  Disk-bearing Stars in NGC 2264 with CoRoT and Spitzer --- Evidence for
  Multiple Origins of Variability}.
\newblock \aj. 2014 Apr;147:82.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2014AJ....147...82C}.

\bibitem{2012AJ....143...72M}
{Mamajek} EE, {Quillen} AC, {Pecaut} MJ, {Moolekamp} F, {Scott} EL, {Kenworthy}
  MA, et~al.
\newblock {Planetary Construction Zones in Occultation: Discovery of an
  Extrasolar Ring System Transiting a Young Sun-like Star and Future Prospects
  for Detecting Eclipses by Circumsecondary and Circumplanetary Disks}.
\newblock \aj. 2012 Mar;143:72.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2012AJ....143...72M}.

\bibitem{2013AJ....146..112R}
{Rodriguez} JE, {Pepper} J, {Stassun} KG, {Siverd} RJ, {Cargile} P, {Beatty}
  TG, et~al.
\newblock {Occultation of the T Tauri Star RW Aurigae A by its Tidally
  Disrupted Disk}.
\newblock \aj. 2013 Nov;146:112.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2013AJ....146..112R}.

\bibitem{1984A&AS...55..109F}
{Finkenzeller} U, {Mundt} R.
\newblock {The Herbig Ae/Be stars associated with nebulosity}.
\newblock \aaps. 1984 Jan;55:109--141.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1984A&AS...55..109F}.

\bibitem{1999AJ....118.1043H}
{Herbst} W, {Shevchenko} VS.
\newblock {A Photometric Catalog of Herbig AE/BE Stars and Discussion of the
  Nature and Cause of the Variations of UX Orionis Stars}.
\newblock \aj. 1999 Aug;118:1043--1060.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1999AJ....118.1043H}.

\bibitem{2000A&A...364..633N}
{Natta} A, {Whitney} BA.
\newblock {Models of scattered light in UXORs}.
\newblock \aap. 2000 Dec;364:633--640.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2000A&A...364..633N}.

\bibitem{2013A&A...557A..77B}
{Bouvier} J, {Grankin} K, {Ellerbroek} LE, {Bouy} H, {Barrado} D.
\newblock {AA Tauri's sudden and long-lasting deepening: enhanced extinction by
  its circumstellar disk}.
\newblock \aap. 2013 Sep;557:A77.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2013A&A...557A..77B}.

\bibitem{2015AJ....150...32R}
{Rodriguez} JE, {Pepper} J, {Stassun} KG, {Siverd} RJ, {Cargile} P, {Weintraub}
  DA, et~al.
\newblock {V409 Tau as Another AA Tau: Photometric Observations of Stellar
  Occultations by the Circumstellar Disk}.
\newblock \aj. 2015 Jul;150:32.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2015AJ....150...32R}.

\bibitem{1999MNRAS.303..521M}
{Mikolajewski} M, {Graczyk} D.
\newblock {Is the eclipsing variable EE CEP a cousin of epsilon Aur?}
\newblock \mnras. 1999 Mar;303:521--524.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1999MNRAS.303..521M}.

\bibitem{2014ApJ...788...41D}
{Dong} S, {Katz} B, {Prieto} JL, {Udalski} A, {Kozlowski} S, {Street} RA,
  et~al.
\newblock {OGLE-LMC-ECL-11893: The Discovery of a Long-period Eclipsing Binary
  with a Circumstellar Disk}.
\newblock \apj. 2014 Jun;788:41.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2014ApJ...788...41D}.

\bibitem{2015ApJS..220...14K}
{Kloppenborg} BK, {Stencel} RE, {Monnier} JD, {Schaefer} GH, {Baron} F,
  {Tycner} C, et~al.
\newblock {Interferometry of {$\epsilon$} Aurigae: Characterization of the
  Asymmetric Eclipsing Disk}.
\newblock \apjs. 2015 Sep;220:14.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2015ApJS..220...14K}.

\bibitem{1988SvAL...14...27G}
{Grinin} VP.
\newblock {On the Blue Emission Visible during Deep Minima of Young Irregular
  Variables}.
\newblock Soviet Astronomy Letters. 1988 Feb;14:27.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1988SvAL...14...27G}.

\bibitem{2001ARep...45...51R}
{Rostopchina} AN, {Grinin} VP, {Shakhovskoi} DN.
\newblock {Photometry and Polarimetry of the Classical Herbig Ae Star VV Ser}.
\newblock Astronomy Reports. 2001 Jan;45:51--59.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2001ARep...45...51R}.

\bibitem{1999A&A...349..619B}
{Bouvier} J, {Chelli} A, {Allain} S, {Carrasco} L, {Costero} R, {Cruz-Gonzalez}
  I, et~al.
\newblock {Magnetospheric accretion onto the T Tauri star AA Tauri. I.
  Constraints from multisite spectrophotometric monitoring}.
\newblock \aap. 1999 Sep;349:619--635.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1999A&A...349..619B}.

\bibitem{1994ASPC...62...63G}
{Grinin} VP.
\newblock {Polarimetric activity of Herbig Ae/Be stars}.
\newblock In: {The} PS, {Perez} MR, {van den Heuvel} EPJ, editors. The Nature
  and Evolutionary Status of Herbig Ae/Be Stars. vol.~62 of Astronomical
  Society of the Pacific Conference Series; 1994. p.~63.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1994ASPC...62...63G}.

\bibitem{2016ApJ...816...69A}
{Ansdell} M, {Gaidos} E, {Rappaport} SA, {Jacobs} TL, {LaCourse} DM, {Jek} KJ,
  et~al.
\newblock {Young ``Dipper'' Stars in Upper Sco and Oph Observed by K2}.
\newblock \apj. 2016 Jan;816:69.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2016ApJ...816...69A}.

\bibitem{2003ApJ...594L..47D}
{Dullemond} CP, {van den Ancker} ME, {Acke} B, {van Boekel} R.
\newblock {Explaining UX Orionis Star Variability with Self-shadowed Disks}.
\newblock \apjl. 2003 Sep;594:L47--L50.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2003ApJ...594L..47D}.

\bibitem{2016arXiv160503985B}
{Bodman} EHL, {Quillen} AC, {Ansdell} M, {Hippke} M, {Boyajian} TS, {Mamajek}
  EE, et~al.
\newblock {Dippers and Dusty Disks Edges: A Unified Model}.
\newblock ArXiv e-prints. 2016 May;Available from:
  \url{http://adsabs.harvard.edu/abs/2016arXiv160503985B}.

\bibitem{2007prpl.conf..539M}
{Millan-Gabet} R, {Malbet} F, {Akeson} R, {Leinert} C, {Monnier} J, {Waters} R.
\newblock {The Circumstellar Environments of Young Stars at AU Scales}.
\newblock Protostars and Planets V. 2007;p. 539--554.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2007prpl.conf..539M}.

\bibitem{1985PZ.....22..181Z}
{Zajtseva} GV.
\newblock {Photometric features of RZ Piscium.}
\newblock Peremennye Zvezdy. 1985;22:181--190.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1985PZ.....22..181Z}.

\bibitem{1999A&AS..140..293G}
{G{\"u}rtler} J, {Friedemann} C, {Reimann} HG, {Splittgerber} E, {Rudolph} E.
\newblock {A comparative study of the long-term light variations of six young
  irregular variables}.
\newblock \aaps. 1999 Dec;140:293--307.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1999A&AS..140..293G}.

\bibitem{2003ARep...47..580S}
{Shakhovskoi} DN, {Grinin} VP, {Rostopchina} AN.
\newblock {Photometric and Polarimetric Activity of RZ Psc}.
\newblock Astronomy Reports. 2003 Jul;47:580--586.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2003ARep...47..580S}.

\bibitem{2010A&A...524A...8G}
{Grinin} VP, {Potravnov} IS, {Musaev} FA.
\newblock {The evolutionary status of the UX Orionis star RZ Piscium}.
\newblock \aap. 2010 Dec;524:A8.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2010A&A...524A...8G}.

\bibitem{2013A&A...553L...1D}
{de Wit} WJ, {Grinin} VP, {Potravnov} IS, {Shakhovskoi} DN, {M{\"u}ller} A,
  {Moerchen} M.
\newblock {Active asteroid belt causes the UXOR phenomenon in RZ Piscium}.
\newblock \aap. 2013 May;553:L1.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2013A&A...553L...1D}.

\bibitem{1980PZ.....21..310K}
{Kardopolov} VI, {Sakhanenok} VV, {Shutemova} NA.
\newblock {On the character of brightness variations of RZ Pisces.}
\newblock Peremennye Zvezdy. 1980;21:310--313.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1980PZ.....21..310K}.

\bibitem{1981Afz....17...87P}
{Pugach} AF.
\newblock {Phenomenological model of the antiflare star RZ PSC}.
\newblock Astrofizika. 1981 Jan;17:87--96.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1981Afz....17...87P}.

\bibitem{2004ARep...48..470P}
{Pugach} AF.
\newblock {Optical Properties of the Circumstellar Dust around Stars with
  Aperiodic Fadings}.
\newblock Astronomy Reports. 2004 Jun;48:470--475.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/2004ARep...48..470P}.

\bibitem{1991Afz....34..333K}
{Kiselev} NN, {Minikulov} NK, {Chernova} GP.
\newblock {Strong increase of the linear polarization of RZ PSC at deep
  minimum.}
\newblock Astrofizika. 1991;34:333--343.
\newblock Available from:
  \url{http://adsabs.harvard.edu/abs/1991Afz....34..333K}.
